---
title: "CO2 Data Analysis in Shiny App"
author: "Anil K. Khadka"
date: "2023-11-14"
output: ioslides_presentation
---

```{r setup, include=FALSE,message=FALSE,warning=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	cache = TRUE,
	tidy = TRUE)
```


## CO2 Data Analysis Shiny App

### Introduction

- Welcome to the CO2 Data Analysis in Shiny App!

- Explore trends and patterns in CO2 concentration.

- Predict Future Concentration



## User Interface

### Summary

- Gives the statistical summary of CO2 concentration for total observed period

### Select Plot Type

- Use the dropdown menu to select the type of plot you want to explore.

- Options: Time Series, Trend, Monthly Boxplot, Trend and Seasonal Components, and Forecast.

### Submit Button

- Click the "Submit" button to generate the selected plot.



## Time Series Plot: Example{.smaller}

#### Selected Plot Type: Time Series

- Displays the CO2 concentration over time.
- X-axis: Date, 
- Y-axis: CO2 concentration (ppm)

```{r, echo=FALSE,warning=F,message=FALSE, fig.align='center', fig.height=4}

library(datasets)
plot(co2, xlab = "Date", 
     ylab = " CO2 concentration (ppm)",
     main = "")

```

##  Shiny App{.smaller}

### Link for Shiny App 

<https://akhadka525.shinyapps.io/ShinyAppProject/>

### Link for GitHub Page

<https://github.com/akhadka525/Developing-Data-Products>

### Data Source and Acknowledgement

- R inbuilt dataset : Mauna Loa Atmospheric CO2 Concentration

- Keeling, C. D. and Whorf, T. P., Scripps Institution of Oceanography (SIO), University of California, La Jolla, California USA 92093-0220.
<https://scrippsco2.ucsd.edu/data/atmospheric_co2/>

### Thank You !!!
